Inspect 3x3 V1

### 2024-10-15 Rmd/Inspect_Outputs/3x3_grid_sample_size_expansion_1.0.Rmd
implement max_length functionality to define the maximum length bin desired in the output. tested - works.

# Introduction
3x3 grid: sample size 10, 20, 30 fixed X expansion none, haul only, haul+month.

@@

## Plot ISS
```{r}

@@

df = tidytable(year = year,
               N10_Enull = out$samples_10$expansion_NULL$length$iss$iss,
               N20_Enull = out$samples_20$expansion_NULL$length$iss$iss,
               N30_Enull = out$samples_30$expansion_NULL$length$iss$iss,
               N10_Eh = out$samples_10$expansion_haul_numbers$length$iss$iss,
               N20_Eh = out$samples_20$expansion_haul_numbers$length$iss$iss,
               N30_Eh = out$samples_30$expansion_haul_numbers$length$iss$iss,
               N10_Ehm = out$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N20_Ehm = out$samples_20$expansion_haul_month_numbers$length$iss$iss,
               N30_Ehm = out$samples_30$expansion_haul_month_numbers$length$iss$iss,)

@@

>>>>

# Introduction
3x3 grid: sample size 10, 20, 30 fixed X expansion none, haul only, haul+month. For both with and without expand by sampling strata.

@@

## Plot ISS
```{r, eval=F}

@@

df = tidytable(year = year,
               N10_Enone = out$samples_10$expansion_NULL$length$iss$iss,
               N20_Enone = out$samples_20$expansion_NULL$length$iss$iss,
               N30_Enone = out$samples_30$expansion_NULL$length$iss$iss,
               N10_Emedium = out$samples_10$expansion_haul_numbers$length$iss$iss,
               N20_Emedium = out$samples_20$expansion_haul_numbers$length$iss$iss,
               N30_Emedium = out$samples_30$expansion_haul_numbers$length$iss$iss,
               N10_Efull = out$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N20_Efull = out$samples_20$expansion_haul_month_numbers$length$iss$iss,
               N30_Efull = out$samples_30$expansion_haul_month_numbers$length$iss$iss,)

@@

## Plot ISS V2.2
```{r}

df = tidytable(year = year,
               N10_Enull = out2$samples_10$expansion_NULL$length$iss$iss,
               N20_Enull = out2$samples_20$expansion_NULL$length$iss$iss,
               N30_Enull = out2$samples_30$expansion_NULL$length$iss$iss,
               N10_Eh = out2$samples_10$expansion_haul_numbers$length$iss$iss,
               N20_Eh = out2$samples_20$expansion_haul_numbers$length$iss$iss,
               N30_Eh = out2$samples_30$expansion_haul_numbers$length$iss$iss,
               N10_Ehm = out2$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N20_Ehm = out2$samples_20$expansion_haul_month_numbers$length$iss$iss,
               N30_Ehm = out2$samples_30$expansion_haul_month_numbers$length$iss$iss,)
